The Warrior Stabs the Goat: Creating a Dothraki Resource Grammar with Grammatical Framework

### 2016-10-16 documentation/paper.tex
Updated docs / some grammar fixes
I added some additional vocabulary and implemented mass nouns
in order to make the example text in the doc a bit nicer.

\usepackage[activate]{pdfcprot}
\usepackage[active]{srcltx}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\fancyhead[RO,LE]{\thepage}
\fancyhead{}
\fancyhead[LE]{\nouppercase{\textssc{\leftmark}}}
\fancyhead[RO]{\nouppercase{\textssc{\rightmark}}}
\fancyfoot[C]{\thepage}
%\fancyfoot[C]{\Pisymbol{MinionPro-Extra}{120} \thepage\ \Pisymbol{MinionPro-Extra}{120}}
%\fancyfoot[LO]{\thepage}
%\fancyfoot[RE]{\thepage}
%\fancyfoot{}

@@

@@

\mainmatter
\section{Introduction}
Grammatical Framework (GF) is a functional programming language, 
created in 1998 \cite{gf-book}, doubling as a categorial grammar 
formalism that can be used to implement (natural) language grammars. 
As GF is ``working from a language-independent representation of meaning''
\cite{wiki-gf}
it can be used to generate or parse text in different languages, 
e.g.\ for use in machine translation. 
Since GF uses a symbolic approach to processing and translating language,
in most cases its translations are more precise than those of the 
more commonly used statistical tools \cite{brown-frederking}. 
For example, on somewhat complicated input,
the ``Google Translate'' service \cite{google} will in many cases
produce ungrammatical sentences, while the GF translator 
\cite{gf-translate} has no problems producing 
a correct translation:

\begin{center}
  \rowcolors{2}{gray!25}{white}
  \begin{tabular}{p{3.7cm}|p{4cm}|p{3.7cm}}
  \rowcolor{gray!50}
    Input & Output Google Translate & Output GF Translator\\\hline
    I heal these women. & 
    Ich diese Frauen zu heilen. & 
    Ich verheile diese Frauen.\\
    The warrior will kiss that cheese behind the tree. & 
    Der Krieger wird Kuss, der K\"ase hinter dem Baum. & 
    Der Krieger wird jenen K\"ase hinter dem Baum k\"ussen.\\
    Diese hei\ss e Frau heilt diese K\"onigin im Meer. & 
    This hot woman heals the queen of the sea.  & 
    This hot woman heals this queen in the sea.
  \end{tabular}
\end{center}

Symbolic formalisms like GF -- unlike Google Translate -- depend 
on a large knowledge base of predefined grammar rules 
to achieve high-quality language processing: Its 
own standard library, the GF Resource Grammar Library, covers 
more than 38 different languages \cite{gf-status} -- although many of 
them are not yet complete -- and is still growing. 
In 2010, it already consisted of more than 500,000 
lines of code \cite{gf-book}. 
As Grammatical Framework is an open-source project \cite{ranta-rgl} 
and still under development, everyone is invited to use it 
or even help further develop it, for example by adding languages to 
the library, which is the aim of the project described in this paper. 
Our goal is to write a GF resource grammar for the Dothraki 
language and, eventually, be able to add it to the GF 
Resource Grammar Library. The work described in this paper is meant to 
lay a foundation for this goal (see Section \ref{sec-goals}).
Dothraki is a constructed language, developed by the language creator and writer 
David J. Peterson \cite{peterson-book}. The Dothraki 
are a fictional race of nomadic horse warriors in the ``A Song of Ice and 
Fire'' book series by George R. R. Martin \cite{martin}. 
As the series was adapted for television by the television network HBO, 
the language bits found in Martin's books had to be extended 
to a fully functional language \cite{peterson-web}: The Dothraki language. 
Today, it has a vocabulary of over 1,400 words 
\cite{vocab}. Examples of 
Dothraki language grammar will appear
in Section \ref{sec-impl}, but much more information can 
be found in the book ``Living Language Dothraki'' \cite{living-language}, 
on Peterson's blog \cite{peterson-web} and on the Tongues of Ice and 
Fire Wiki (2016) among many other sources.

@@

\begin{quote}
The idea of using a grammar as a software library is, to our knowledge,
new in GF. It has required a considerable effort in the design 
and implementation of the GF programming language: a type system, 
a module system, compilation techniques, and optimizations. [...] 
The  effort
made in this work is supplemented by a substantial effort in the 
library itself.
The code included in the library is more than twice in size compared to the
implementation of GF.\hfill\cite{ranta-rgl}
\end{quote} 
This division of labour benefits not just the application programmers,
however, but also the linguistics experts implementing the 
application-independent libraries:\\ Firstly, because a resource 
grammar, once written, can ``serve an unlimited number of applications'' 
\cite[p.\ 200]{gf-book}, but also because ``the existing library 
specification will help to identify the linguistic issues 
and avoid pitfalls'' by providing a well thought-out, 
language-independent interface.

@@

\begin{figure}[h]
\begin{itemize}[itemsep=0.5pt]
\item simpleapi
\item simpleabstract
\item simpledothraki
\item simpleenglish
\item common

@@

\vspace{0.2cm}
\item documentation 
\item vocabulary
\end{itemize}
\caption{\label{fig-folders}The project's folder structure}
\end{figure}

@@

\begin{figure}
\begin{tabular}{l|l}
\begin{minipage}{.44\linewidth}
\begin{lstlisting}
*'''aranikh''' [a?a'nix]
:''ni.'' subject, topic, theme

@@

There are a total of 1,916 English translations in the vocabulary list.
The script is able to extract 1,059 entries for \name{BigLexicon}
from this. Many translations cannot be directly added to
\name{BigLexicon} for various reasons:
\begin{itemize}
  \item Some English words appear as translations for
  more than one Dothraki word. The script picks the first
  one it finds.\footnote{Obviously, that might not result in the
  best or most appropriate translation being picked, but that issue
  can be addressed by later manual editing of the generated list.}
  \item Many Dothraki words do not correspond to any one English word.
  For example the list contains entries for ``defensive sword strike'',
  ``sound of fire going out'', ``roast quail'' or
  ``time period of approximately two minutes''. While for some of these,
  it might be desirable to have dictionary 
  entries,\footnote{For example, there could be an entry
  §roast_quail_CN : CN§ in \name{BigLexicon} with linearizations
  §roast_quail_CN = mkCN DictEng.roast_A (mkCN DictEng.quail_N)§
  in
  \name{BigLexiconEng} and §roast_quail_CN = mkCN DictDot.mechikh_N§
  in \name{BigLexiconDot}.} this process is almost impossible
  to automate and must be done by hand.
\end{itemize}

@@

The multiple outputs for the last command are 
quite typical and derive from the fact that the parse of the English 
sentence is ambiguous:
Was the duck stabbed with a dagger or was a duck with a dagger stabbed?
Note that, in this case, the Dothraki translations differ, because the
possessive pronoun ``anni'' follows the noun phrase
(either ``dorv'' = ``goat'' or ``dorv ma mihesofoon'' = ``goat with a dagger'').

@@

\subsection{Limitations}
As Ranta notes in \cite{gf-slides}, the most important
sources for creating a resource grammar are
``[a] \emph{good} grammar book'' and ``[a] \emph{good} dictionary''.

That poses some problems in the case of Dothraki.
There are basically only two sources of information
on Dothraki grammar: The writings of inventor 
David J.\ Peterson \cite{peterson-web},
the community-operated ``Tongues of Ice and Fire`` wiki
at \url{wiki.dothraki.org}. These tend to be great resources
for the basic parts of the language. Peterson's
blog contains detailed, accessible explanations of
many grammatical phenomena featured in
the snippets of Dothraki, that have appeared on the show
up to its third season. And the enthusiastic Dothraki community
has done great work organizing and detailing this information.

However, as our work progressed, it has become harder and harder
to find good information on some of the more subtle or
obscure parts of the grammar. It should be noted that the
total corpus of text in the Dothraki language 
still comprises only a few hundred sentences.
By now, we have already mostly
incorporated the information available from the two sources
mentioned above (the two largest remaining omissions are wh-questions and
numerals). In many cases we have run up against the limits
of what information is available and sometimes we have been
forced to resort to the Dothraki corpus itself
in an effort to try and reverse engineer
language features that so far have not been explained by
their inventor.

@@

  When they have appeared on the show, verb phrase
  complements are usually avoided in favour of
  embedded clauses:

@@

  \item The module \name{Structural} contains a number
  of common structural words that should be available in 
  every language. Quite a few of these are simply not yet
  available in Dothraki (``somewhere'', ``almost'',
  ``quite'', ``otherwise'', ``at least'' etc.), but
  even those that have translations in the vocabulary list
  are sometimes difficult to implement. For example, the
  vocabulary list notes that ``someone'' translates as
  ``ato''. But since this is a noun phrase, it probably
  must inflect somehow.
  Inflection in nouns depends on their animacy, but
  it is not clear whether inanimate or animate declension
  is used here (or some irregular inflection, as with determiners). 
  In the corpus ``ato'' appears exactly once,
  in the nominative. In the end, we had no other choice
  but to guess the declension (we decided on standard
  animate inflection).

  Similarly, ``eyak'' supposedly means ``everybody'', according
  to the vocabulary, but in the only place it is used
  in the corpus, it seems to be used in the sense of ``everything''.
  In that instance it is used in the genitive (probably; the phrase
  is ``hatif eyaki'' and the preposition ``hatif'' can assign
  genitive, allative or ablative case, depending on meaning).
  In the end we decided on a declension based on this one occurence and
  by analogy with ``vosak'' (= ``nobody''), which occurs in
  the accusative once.

@@

\subsection{Outlook}
In the future, we would like to expand our resource grammar to a
full resource grammar and add it to the GF resource grammar library.
We are already working on and hosting the project online, for everyone
to see, so that the GF and/or Dothraki community may help us to achieve
this goal. Some more parts we can implement right now, for some we have
to wait until more information regarding the Dothraki language is being
published. In the end, we also want to add the full vocabulary to our
dictionary.

\subsection{Conclusion}
Now that the first milestone of our project lies behind us,
we can evaluate the working process and the result. As we had
some starting problems at the beginning of the project, we are
proud to have been able to create such a big portion of the
resource grammar in the given time. By relying on the basics
learned during the seminar and by aiming for such an ambitious
goal, we surely learned a lot during the process. As we are
convinced that our project can be helpful and interesting for
other people in the future, we were motivated to keep on working
on the resource grammar and to try to find the best solution for
every problem. This term paper does not mark the end of this project,
but we are curious to hear what you, our lecturers, and other people
think of the work we have done so far.

>>>>

%\usepackage[activate]{pdfcprot}
\usepackage{microtype}
\usepackage[active]{srcltx}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\fancyhead[RO,LE]{\thepage}
\fancyhead{}
\fancyhead[LE]{\nouppercase{\textssc{\leftmark}}}
\fancyhead[RO]{\nouppercase{\textssc{\rightmark}}}
\fancyfoot[C]{\thepage}
%\fancyfoot[C]{\Pisymbol{MinionPro-Extra}{120} \thepage\ \Pisymbol{MinionPro-Extra}{120}}
%\fancyfoot[LO]{\thepage}
%\fancyfoot[RE]{\thepage}
%\fancyfoot{}

@@

\usepackage{breakcites}

@@

\mainmatter
\section{Introduction}
Grammatical Framework (GF) is a functional programming language, 
created in 1998 \cite{gf-book}, doubling as a categorial grammar 
formalism that can be used to implement (natural) language grammars. 
As GF is ``working from a language-independent representation of meaning''
\cite{wiki-gf}
it can be used to generate or parse text in different languages, 
e.g.\ for use in machine translation. 
Since GF uses a symbolic approach to processing and translating language,
in most cases its translations are more precise than those of the 
more commonly used statistical tools \cite{brown-frederking}. 
For example, on somewhat complicated input,
the ``Google Translate'' service \cite{google} will in many cases
produce ungrammatical or wrong translations, while the GF translator 
\cite{gf-translate} has no problems producing 
a correct translation (as of 22 September 2016):

\begin{center}
  \rowcolors{2}{gray!25}{white}
  \begin{tabular}{p{3.7cm}|p{4cm}|p{3.7cm}}
  \rowcolor{gray!50}
    Input & Output Google Translate & Output GF Translator\\\hline
    Ich komme im Krieg um. & I'm in the war. & I die in the war.\\
    Ich denke in der Vorlesung immer nach, bevor ich rede. &
    I always think about the lecture before I speak. &
    I always think in the lecture, before I talk.\\
    I heal these women. & 
    Ich diese Frauen zu heilen. & 
    Ich verheile diese Frauen.\\
    The warrior will kiss that cheese behind the tree. & 
    Der Krieger wird Kuss, der K\"ase hinter dem Baum. & 
    Der Krieger wird jenen K\"ase hinter dem Baum k\"ussen.\\
    Diese hei\ss e Frau heilt diese K\"onigin im Meer. & 
    This hot woman heals the queen of the sea.  & 
    This hot woman heals this queen in the sea.
  \end{tabular}
\end{center}

Symbolic formalisms like GF -- unlike Google Translate -- depend 
on a large knowledge base of predefined grammar rules 
to achieve high-quality language processing:\footnote{As can be seen
when trying to translate grammatical constructions that are not 
explicitly covered by GF's grammar rules.
For a taste of this, try translating ``Die Krone der K\"onigin ist sch\"on''
or ``Das Buch, das die Frau mir gab, war alt'' to English using the
GF translator (possessive constructions and object
relativization for verbs taking more than one object are currently
not covered satisfactorily in GF's abstract grammar model).}
Its 
own standard library, the GF Resource Grammar Library, covers 
more than 38 different languages \cite{gf-status} -- although many of 
them are not yet complete -- and is still growing. 
In 2010, it already consisted of more than 500,000 
lines of code \cite{gf-book}. 
As Grammatical Framework is an open-source project \cite{ranta-rgl} 
and still under development, everyone is invited to use it 
or even help further develop it, for example by adding languages to 
the library, which is the aim of the project described in this paper. 
Our goal is to write a GF resource grammar for the Dothraki 
language and, eventually, be able to add it to the GF 
Resource Grammar Library. The work described in this paper is meant to 
lay a foundation for this goal (see Section \ref{sec-goals}).
Dothraki is a constructed language, developed by the language creator and writer 
David J. Peterson \cite{peterson-book}. The Dothraki 
are a fictional race of nomadic horse warriors in the ``A Song of Ice and 
Fire'' book series by George R. R. Martin \cite{martin}. 
As the series was adapted for television by the television network HBO, 
the language bits found in Martin's books had to be extended 
to a fully functional language \cite{peterson-web}: The Dothraki language. 
Today, it has a vocabulary of over 1,400 words 
\cite{vocab}. Examples of 
Dothraki language grammar will appear
in Section \ref{sec-impl}, but much more information can 
be found in the book ``Living Language Dothraki'' \cite{living-language}, 
on Peterson's blog \cite{peterson-web} and on the Tongues of Ice and 
Fire Wiki (2016) among many other sources.

@@

\begin{quote}
The idea of using a grammar as a software library is, to our knowledge,
new in GF. It has required a considerable effort in the design 
and implementation of the GF programming language: a type system, 
a module system, compilation techniques, and optimizations. [...] 
The  effort
made in this work is supplemented by a substantial effort in the 
library itself.
The code included in the library is more than twice in size compared to the
implementation of GF.\hfill\cite{ranta-rgl}
\end{quote} 
This division of labour benefits not just the application programmers,
however, but also the linguistics experts implementing the 
application-independent libraries: Firstly, because a resource 
grammar, once written, can ``serve an unlimited number of applications'' 
\cite[p.\ 200]{gf-book}, but also because ``the existing library 
specification will help to identify the linguistic issues 
and avoid pitfalls'' by providing a well thought-out, 
language-independent interface.

@@

\begin{figure}[h]
\centering
\fbox{
\begin{minipage}{5cm}
\begin{itemize}[itemsep=0.5pt]
\item simpleapi
\item simpleabstract
\item simpledothraki
\item simpleenglish
\item common

@@

\vspace{0.2cm}
\item documentation 
\item vocabulary
\end{itemize}
\end{minipage}
}
\caption{\label{fig-folders}The project's folders}
\end{figure}

@@

\begin{figure}[t]
\begin{tabular}{l|l}
\begin{minipage}{.44\linewidth}
\begin{lstlisting}
*'''aranikh''' [a?a'nix]
:''ni.'' subject, topic, theme

@@

There are a total of 1,916 English translations in the vocabulary list.
The script is able to extract 1,130 entries for \name{BigLexicon}
from this. Many translations cannot be directly added to
\name{BigLexicon} for various reasons:
\begin{itemize}
  \item Some English words appear as translations for
  more than one Dothraki word. The script picks the first
  one it finds.\footnote{Obviously, that might not result in the
  best or most appropriate translation being picked, but that issue
  can be addressed by later manual editing of the generated list.}
  \item Many Dothraki words do not correspond to any one English word.
  For example the list contains entries for ``defensive sword strike'',
  ``sound of fire going out'', ``roast quail'' or
  ``time period of approximately two minutes''. While for some of these,
  it might be desirable to have dictionary 
  entries,\footnote{For example, there could be an entry
  §roast_quail_CN : CN§ in \name{BigLexicon} with linearizations
  §roast_quail_CN = mkCN DictEng.roast_A (mkCN DictEng.quail_N)§
  in
  \name{BigLexiconEng} and §roast_quail_CN = mkCN DictDot.mechikh_N§
  in \name{BigLexiconDot}.} this process is almost impossible
  to automate and must be done by hand.
\end{itemize}

As an example of how extra vocabulary, that cannot be automatically
extracted from the vocabulary list, can be supplied manually the module 
\name{ExtraLex\emph{XXX}} contains a (currently minimal) sampling of
additional words.

@@

The multiple outputs for the last command are 
quite typical and derive from the fact that the parse of the English 
sentence is ambiguous:
Was the duck stabbed with a dagger or was a duck with a dagger stabbed?
Note that, in this case, the Dothraki translations differ, because the
possessive pronoun ``anni'' follows the noun phrase
(either ``dorv'' = ``goat'' or ``dorv ma mihesofoon'' = ``goat with a 
dagger'').\footnote{There are often \emph{lots} of different parses when
parsing Dothraki sentences. Dothraki has no articles,
does not distinguish between he/she/it and rarely distinguishes
singular and plural for inanimate nouns. The sentence
``Me vindee dorv'' can mean ``He stabs the goat'', ``She stabs the goat'',
``He stabs goats'', etc. The three possible choices for ``me'' and
five possible choices for ``dorv'' (singular/plural definite/indefinite article  or mass noun) 
already give fifteen parses and that's
not even counting all the \emph{really} strange interpretations
deriving from the fact that ``vindee'' could also be the future 
tense of ``indelat'' = ``to drink''...}

Here is a more elaborate example:\footnote{The sentences are lightly editted compared
to the parser input/output, to account for the
fact that the lexer requires spaces around
punctuation and first words of sentences may not be capitalized.
There are also usually multiple possible parses, in which case we picked
the most appropriate one.}

\begin{quote}
I found this woman on the mountain, Khal Drogo. 
She was asleep and there was a dead lizard behind her. 
Its head had been cut off. 
She is a sorceress! 
They squeeze the blood from the lizard and they drink it. 
Then they crush the bones and they cook them with many roots and the fresh skins of snakes. 
It is known. 
She will try to poison you! 
Do you believe me? 
Therefore you must kill her! 
Don't listen to her. 
A woman who cooks poison mustn't survive. 
She is dangerous. 
Everybody knows. 
You are the leader whom the horde respects. 
Cut her throat with your arakh! 
\end{quote}

\begin{quote}
Anha ez jinakes chiories she krazaaj, zhey Khal Drogo.
Me remek ma zhavi driva irge mae vekh.
Nhare mae nem ray zirisse.
Mori efi qoy ha zhavoon ma mori indee mae.
Hash mori kaffi tolor ma mori jolini mora ma ma sanoon garfothoon ma ilekoon choshi gezrisi.
Me nem nesa.
Me kis vizza shafka!
Hash shafka shilloe anna?
Majin shafka eth addrivi mae!
Vos charos maan.
Chiori fin jolina iz eth vos thiroo.
Me zhowaka.
Eyak nesa.
Shafka akkelenak finnaan choma khalasar.
Rissas foth mae ma arakhoon shafki!
\end{quote}

It demonstrates the following
features supported by our resource grammar:
\begin{itemize}[itemsep=0pt]
  \item Transitive and intransitive verbs
  \item Tenses: Past perfect, present, future, present perfect, past perfect
  \item Negation
  \item Passive voice
  \item Verbal auxiliaries
  \item Imperatives
  \item Personal pronouns
  \item Demonstratives
  \item Possessive pronouns
  \item Existential clauses
  \item Adverbial phrases with prepositions
  \item Zero-copula sentences
  \item Adjectives (attributive and predicative)
  \item Relative clauses (both subject and object relativization)
  \item Proper names
  \item Mass nouns
  \item Vocatives
  \item Yes/no questions
  \item Conjunctions (for noun and verb phrases)
  \item Phrasal conjunctions
  \item Structural words (every, many, somebody, nobody, ...)
\end{itemize}

@@

\subsection{Limitations}\label{sec-lim}
As Ranta notes in \cite{gf-slides}, the most important
sources for creating a resource grammar are
``[a] \emph{good} grammar book'' and ``[a] \emph{good} dictionary''.

That poses some problems in the case of Dothraki.
There are basically only two sources of information
on Dothraki grammar: The writings of inventor 
David J.\ Peterson \cite{peterson-web} and
the community-operated ``Tongues of Ice and Fire`` wiki
at \url{wiki.dothraki.org}. To be sure, these tend to be great resources
for the basic parts of the language. Peterson's
blog contains detailed, accessible explanations of
many grammatical phenomena featured in
the snippets of Dothraki that have appeared on the show
up to its third season. And the enthusiastic Dothraki community
has done tremendous work in organizing and detailing this information.

However, as our work progressed, it has become harder and harder
to find good information on some of the more subtle or
obscure parts of the grammar. It should be noted that the
total corpus of text in the Dothraki language 
still comprises only a few hundred sentences.
By now, we have already mostly
incorporated the information available from the two sources
mentioned above. In many cases we have run up against the limits
of what information is available and sometimes we have been
forced to resort to the Dothraki corpus itself
in an effort to try and reverse engineer
language features that so far have not been explained by
their inventor.

@@

  Where §VV§s do appear in the corpus, verb phrase
  complements are usually avoided in favour of
  embedded clauses:

@@

  The problem is only more pronounced for the even more
  obscure categories of verbs, such as §VA§, §VQ§, §V2A§, §V2Q§,
  or §V2S§.\footnote{To give an idea: Of the around 65,000 words in \name{DictEng},
  there are 49 of type §VA§, 7 of type §VQ§, 15 of type §V2A§, four of type
  §V2S§ and one of type §V2Q§. Obviously, evidence of usage of such words in the
  Dothraki corpus is scarce.}

  \item The module \name{Structural} contains a number
  of common structural words that should be available in 
  every language. Quite a few of these are simply not yet
  available in Dothraki (``somewhere'', ``almost'',
  ``quite'', ``otherwise'', ``at least'' etc.), but
  even those that have translations in the vocabulary list
  are sometimes difficult to implement. For example, the
  vocabulary list notes that ``someone'' translates as
  ``ato''. But since this is a noun phrase, it probably
  must inflect for case somehow.
  Inflection in nouns depends on their animacy, but
  it is not clear whether inanimate or animate declension
  is used here (or some irregular inflection, as with determiners). 
  In the corpus, ``ato'' appears exactly once,
  in the nominative, thus giving no useful hints. In the end, we had no other choice
  but to guess the declension (we decided on standard
  animate inflection).

  Similarly, ``eyak'' supposedly means ``everybody'', according
  to the vocabulary, but no declension is given and the word appears
  only once in the corpus.\footnote{and curiously,
  it seems to be used more in the sense of ``everything''}
  In that instance it is used in the genitive (probably; the phrase
  is ``hatif eyaki'' and the preposition ``hatif'' can assign
  genitive, allative or ablative case, depending on meaning).
  In the end we decided on a declension based on this one occurence and
  by analogy with ``vosak'' (= ``nobody''), which occurs in
  the accusative once.

@@

\subsection{Outlook}
The obvious goal for the future of our project is to expand the
resource grammar further, hopefully to a point where it can eventually be added
to the GF resource grammar library.
We are already working on and hosting the project online, for everyone
to see, so that the GF and/or Dothraki community may help us to achieve
this goal. Some parts could probably be implemented right now 
(the largest omissions right now being wh-questions and numerals; 
§V3§s and reflexive verbs would be useful, too, but their implementation 
would likely
run up against some of the problems laid out in Section \ref{sec-lim}), 
for some we have
to wait until more information regarding the Dothraki language is being
published. Finally, it would also be useful to improve the dictionary
by augmenting our current automatic extraction approach with
some manual curation.

\subsection{Conclusion}
Now that the first milestone of our project lies behind us,
we can evaluate the working process and the result. After having
overcome our initial problems setting up the project, we are
proud of having been able to create such a big portion of the
resource grammar in the given time. By relying on the basics
learned during the seminar and by aiming for such an ambitious
goal, we surely learned a lot during the process. As we are
convinced that our project can be useful and interesting for
other people in the future, we were motivated to keep on working
on the resource grammar and to try to find the best solution for
every problem. This term paper does not mark the end of this project,
but we are curious to hear what you, our lecturers, and other people
think of the work we have done so far.
